Future Cosmic Microwave Background delensing with galaxy surveys.

### 2017-07-10 Notes/galaxy_delensing.tex
refs

For LSST we follow \cite{schaan:2016}: $\frac{dN}{dz}\propto z^{\alpha}\exp^{-(z/z_{0})^{\beta}}$ with $\alpha = 1.27$, $\beta = 1.02$, and $z_{0}= 0.5$. Furthermore we assume a density of 26 galaxies per arcmin squared.

>>>>

For LSST we follow \cite{schaan:2017}: $\frac{dN}{dz}\propto z^{\alpha}\exp^{-(z/z_{0})^{\beta}}$ with $\alpha = 1.27$, $\beta = 1.02$, and $z_{0}= 0.5$. Furthermore we assume a density of 26 galaxies per arcmin squared.
